---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: 
  - paperwidth=8.5in
  - paperheight=11in
  - margin=0.05in 
 
header-includes:
  \usepackage{fontspec}
  \setmainfont{Arial}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{/Users/garrettkemp/Documents/Mercer Baseball/Photos for Graphics/Sailor-Bear}}
---

```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(scales)
library(pandoc)
library(ggrepel)
library(ggplot2)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=2cm, height=2cm]{SailorBearOG}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\begin{center}
\textbf{\fontsize{20}{20}\selectfont Umpire Report}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=3cm, height=2cm]{SoConLogo}
\end{minipage}

\vspace{-6mm}
\begin{center}
\textbf{\fontsize{16}{16}\selectfont Accuracy: `r gsub('%', '\\\\%', params$accuracy)`}
\end{center}

\vspace{0mm} 
\begin{center}
\textbf{\normalsize `r params$date` Mercer vs `r params$opponent`}
\end{center}

\begin{center}
\textbf{\normalsize This report is based on a standardized strike zone. 
Data points on the graph do not represent the actual size of a baseball. 
Accuracy and missed calls are based on the size of the baseball in relation to 
the strike zone and "buffer zone".}
\end{center}
\vspace{0mm} 

\begin{center}
\textbf{\normalsize Game Stats}
\end{center}
\vspace{-2mm} 

```{r Game Stats, message=FALSE, warning=FALSE}

game_stats %>% 
  kable(format = "latex",  linesep = "", align = 'c') %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>% 
  column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = case_when(
                game_stats$PitchCall == "Strike" ~ '#d22d49',
                game_stats$PitchCall == "Ball" ~ '#00d1ed',
                TRUE ~ 'black'
              )
  ) %>% 
  row_spec(row = 0, color = "white", background = "#f76800") %>%
  column_spec(ncol(game_stats), border_right = TRUE) 



```
\vspace{0mm}
```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 4, fig.align='center'} 
gridExtra::grid.arrange(overall_performance_plot, missed_calls_plot, ncol = 2)
```
\vspace{0mm}
```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 4, fig.align='center'} 
gridExtra::grid.arrange(missed_balls_plot, missed_strikes_plot, ncol = 2)
```
\newpage

```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 4, fig.align='center'} 
gridExtra::grid.arrange(missed_call_situations_plot, missed_call_distance_plot, ncol = 2)
```

```{r Missed Calls, message=FALSE, warning=FALSE}

missed_call_list %>% 
  kable(format = "latex",  linesep = "", align = 'c') %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>% 
  column_spec(1, border_left = TRUE) %>% 
  row_spec(row = 0, color = "white", background = "#f76800") %>%
  column_spec(ncol(missed_call_list), border_right = TRUE) %>% 
  row_spec(nrow(missed_call_list), border_bottom = )

```
